---
title: "Analyse_Benchmark"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---


# Setup

## User-defined file paths

```{r Define paths}

# Input Paths

CCSD_data_dir <- "CCSD/Data/"
DFT_data_dir <- "DFT/Data/"

critical_points <- tibble(
  name = c(
    "transG_g-exo",
    "transG_g-endo",
    "cisD_g-exo",
    "cisA_g-endo",
    "syn-endo",
    "syn-exo",
    "anti-exo",
    "anti-endo"
  ),
  critical_point = c(
    "Minimum",
    "Minimum",
    "Minimum",
    "Minimum",
    "TS",
    "TS",
    "TS",
    "TS"
  ),
  )

functionals = c(
  "B97M-V",
  "B97M-D4",
  "r2SCAN_D3BJ",
  "wB97X-D4rev",
  "wB97X-V",
  "M062X_D3ZERO",
  "PBE0_D3BJ",
  "wB97M-V",
  "wB97M-D4rev",
  "DSD-BLYP_D3BJ"
)

basis_sets = c("def2-TZVPP", "def2-QZVPP")


# Output Paths

extrapolate_rxn_energy_plot_path <- "CCSD/Data/rxn_extrapolation.png"
extrapolate_barrier_plot_path <- "CCSD/Data/barrier_extrapolation.png"
extrapolate_table_path <- "CCSD/Data/extrapolation_table.csv"

DFT_error_plot_path <- "DFT/Data/DFT_deviation.png"
DFT_rxn_basis_set_plot_path <- "DFT/Data/rxn_basis_set_dependance.png"
DFT_barrier_basis_set_plot_path <- "DFT/Data/barrier_basis_set_dependance.png"
rxn_dispersion_plot_path <- "DFT/Data/rxn_dispersion.png"
barrier_dispersion_plot_path <- "DFT/Data/barrier_dispersion.png"

```

## Load required libraries

```{r import libraries}

library(tidyverse)
library(hrbrthemes)
library(jsonlite)
library(cetcolor)
library(ggtext)
library(ggsci)
library(legendry)
library(ggh4x)

```

# Execute program

## CCSD 

### Import Properties

```{r import CCSD Properies}

CCSD_energies <- tibble()

for (i in 1:length(critical_points$name)) {
  path <- paste0(
    CCSD_data_dir,
    "CCSD_",
    critical_points$name[i],
    ".property.json"
    )
  json <- read_json(
    path,
    simplifyVector = FALSE
  )
  row <- tibble(
    "Source" = critical_points$name[i],
     "CCSD_Ano-2_SCF" = json[["Geometry_1"]][["SCF_Energy"]][[1]][["SCF_ENERGY"]],
     "DLPNO_Ano-2_SCF" = json[["Geometry_1"]][["SCF_Energy"]][[2]][["SCF_ENERGY"]],
     "DLPNO_Ano-3_SCF" = json[["Geometry_1"]][["SCF_Energy"]][[3]][["SCF_ENERGY"]],
     "DLPNO_Ano-4_SCF" = json[["Geometry_1"]][["SCF_Energy"]][[4]][["SCF_ENERGY"]],
     "CCSD_Ano-2_CORR" = json[["Geometry_1"]][["MDCI_Energies"]][[1]][["CORRENERGY"]],
     "DLPNO_Ano-2_CORR" = json[["Geometry_1"]][["MDCI_Energies"]][[2]][["CORRENERGY"]],
     "DLPNO_Ano-3_CORR" = json[["Geometry_1"]][["MDCI_Energies"]][[3]][["CORRENERGY"]],
     "DLPNO_Ano-4_CORR" = json[["Geometry_1"]][["MDCI_Energies"]][[4]][["CORRENERGY"]],
     "CCSD_Ano-2_TOTAL" = json[["Geometry_1"]][["MDCI_Energies"]][[1]][["TOTALENERGY"]],
     "DLPNO_Ano-2_TOTAL" = json[["Geometry_1"]][["MDCI_Energies"]][[2]][["TOTALENERGY"]],
     "DLPNO_Ano-3_TOTAL" = json[["Geometry_1"]][["MDCI_Energies"]][[3]][["TOTALENERGY"]],
     "DLPNO_Ano-4_TOTAL" = json[["Geometry_1"]][["MDCI_Energies"]][[4]][["TOTALENERGY"]],
     "CBS_SCF" = json[["Geometry_1"]][["Energy_Extrapolation"]][["SCFCBS"]],
     "CBS_CORR" = json[["Geometry_1"]][["Energy_Extrapolation"]][["CORRCBS"]],
     "CBS_TOTAL" = json[["Geometry_1"]][["Energy_Extrapolation"]][["TOTALCBS"]],
     "Critical Point" = critical_points$critical_point[i]
  )
  CCSD_energies <- bind_rows(
    CCSD_energies,
    row
  ) 
}


rm(row, json)
```

### Calculate relative energies

```{r CCSD Relative Energies}

CCSD_energies <- CCSD_energies %>%
  mutate(
    "CBS_correction" = `CCSD_Ano-2_CORR`-`DLPNO_Ano-2_CORR`,
    "CCSD_Ano-2_deviation" = `CCSD_Ano-2_CORR`-`DLPNO_Ano-2_CORR`
    )

reference <- CCSD_energies %>%
  filter(CBS_TOTAL == min(CBS_TOTAL)) %>%
  pivot_longer (
  cols = !Source & !`Critical Point`,
  names_pattern =  "(.*)_(.*)",
  names_to = c(
    "Level of Theory",
    "Component"
  ),
  values_to = "Reference Energy"
) %>%
  select(!Source & !`Critical Point`)



CCSD_energies <- CCSD_energies %>%
  pivot_longer (
  cols = !Source & !`Critical Point`,
  names_pattern =  "(.*)_(.*)",
  names_to = c(
    "Level of Theory",
    "Component"
  ),
  values_to = "Energy"
) %>%
  left_join(
    reference
  ) %>%
  mutate(
    Energy = (Energy-`Reference Energy`)*627.5094740631
  ) %>% 
  pivot_wider(
  id_cols = Source | `Level of Theory`|`Critical Point`,
  names_from = Component,
  values_from = Energy,
  unused_fn = first
  ) %>% 
  mutate(
    Source = case_match(
      Source,
      "anti-exo" ~ "<i>anti-exo</i>",
      "syn-exo" ~ "<i>syn-exo</i>" ,
      "anti-endo" ~ "<i>anti-endo</i>",
      "syn-endo" ~ "<i>syn-endo</i>",
      "transG_g-exo" ~ "<i>trans</i>-G<sub>γ</sub>",
      "transG_g-endo" ~ "<i>trans</i>-<sup>γ</sup>G",
      "cisD_g-exo" ~ "<i>cis</i>-D<sub>γ</sub>",
      "cisA_g-endo" ~ "<i>cis</i>-<sup>γ</sup>A",
      .default = Source
    )
  )

CBS_Energies <- CCSD_energies %>%
  filter(`Level of Theory` == "CBS") %>% 
  select(
    Source,
    `Critical Point`,
    TOTAL
    ) %>%
  mutate(
    "CBS_REFERENCE_ENERGY" = TOTAL,
    .keep = "unused"
  )


# TABULATE EXTRAPOLATION

CCSD_energies %>%
  filter(`Level of Theory` == "CBS") %>%
  mutate(
    "Conformation" = gsub("<.{1,4}>", "", Source),
    "Extrapolated SCF Energy" = SCF,
    "Extrapolated Correlation Energy" = CORR,
    "DLPNO Correlation Correction" = correction,
    "Total CBS Energy" = TOTAL,
    .keep = "none"
  ) %>%
  arrange(`Total CBS Energy`) %>%
  write_csv(
    extrapolate_table_path
  )

```


### Prepare Extrapolation Plots

```{r Prepare Extrapolation Plots}

plot_data <- CCSD_energies %>%
  mutate(
    `Level of Theory` = case_match(
      `Level of Theory`,
      "CCSD_Ano-2" ~ "CCSD(T)/ano-pVDZ",
      "DLPNO_Ano-2" ~ "DLPNO-CCSD(T)/ano-pVDZ",
      "DLPNO_Ano-3" ~ "DLPNO-CCSD(T)/ano-pVTZ",
      "DLPNO_Ano-4" ~ "DLPNO-CCSD(T)/ano-pVQZ",
      "CBS" ~ "CCSD(T)/CBS"
    ),
    `Level of Theory` = factor(
      `Level of Theory`, 
      levels = 
        rev(c(
        "CCSD(T)/ano-pVDZ",
        "DLPNO-CCSD(T)/ano-pVDZ",
        "DLPNO-CCSD(T)/ano-pVTZ",
        "DLPNO-CCSD(T)/ano-pVQZ",
        "CCSD(T)/CBS"
        )
      
      )),
    Source = factor(
      Source,
      levels = 
        c(
          "<i>trans</i>-G<sub>γ</sub>",
          "<i>trans</i>-<sup>γ</sup>G",
          "<i>cis</i>-D<sub>γ</sub>",
          "<i>cis</i>-<sup>γ</sup>A",
          "<i>anti-exo</i>",
          "<i>syn-exo</i>",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>"
      )
    
    )
  ) 


cardinal_number <- function(x) {
  if (grepl("pVDZ$", x)) {
    return(2)
  } else if (grepl("pVTZ$", x)) {
    return(3)
  } else if (grepl("pVQZ$", x))  {
    return(4)
  } else if (grepl("CBS$", x))  {
    return(Inf)
  }
  }

alpha <- 4.480
beta <- 2.970 

e <- function(x) {
  exp(-alpha*sqrt(x))
}

extrapolate_SCF <- function(x, CBS, QZ) {
  CBS + e(x)*(QZ-CBS)/e(4)
}

extrapolate_CORR <- function(x, CBS, QZ) {
  CBS + (QZ-CBS)*4^beta/x^beta
}

extrapolate_both <- function(x, CBS_CORR, QZ_CORR, CBS_SCF, QZ_SCF) {
  extrapolate_SCF(x, CBS_SCF, QZ_SCF) + 
  extrapolate_CORR(x, CBS_CORR, QZ_CORR)
}

plot_data <- CCSD_energies %>%
  mutate(
    `Level of Theory` = case_match(
      `Level of Theory`,
      "CCSD_Ano-2" ~ "CCSD(T)/ano-pVDZ",
      "DLPNO_Ano-2" ~ "DLPNO-CCSD(T)/ano-pVDZ",
      "DLPNO_Ano-3" ~ "DLPNO-CCSD(T)/ano-pVTZ",
      "DLPNO_Ano-4" ~ "DLPNO-CCSD(T)/ano-pVQZ",
      "CBS" ~ "CCSD(T)/CBS"
    ),
    `Level of Theory` = factor(
      `Level of Theory`, 
      levels = 
        rev(c(
          "CCSD(T)/ano-pVDZ",
          "DLPNO-CCSD(T)/ano-pVDZ",
          "DLPNO-CCSD(T)/ano-pVTZ",
          "DLPNO-CCSD(T)/ano-pVQZ",
          "CCSD(T)/CBS"
        )
        
        )),
    Source = factor(
      Source,
      levels = 
        c(
          "<i>trans</i>-G<sub>γ</sub>",
          "<i>trans</i>-<sup>γ</sup>G",
          "<i>cis</i>-D<sub>γ</sub>",
          "<i>cis</i>-<sup>γ</sup>A",
          "<i>anti-exo</i>",
          "<i>syn-exo</i>",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>"
        )
      
    ),
    Rank =  case_match(
      Source,
      "<i>trans</i>-G<sub>γ</sub>" ~ 1,
      "<i>trans</i>-<sup>γ</sup>G" ~ 2,
      "<i>cis</i>-D<sub>γ</sub>" ~ 3,
      "<i>cis</i>-<sup>γ</sup>A" ~ 4,
      "<i>anti-exo</i>" ~ 1,
      "<i>syn-exo</i>" ~ 2,
      "<i>anti-endo</i>" ~ 3,
      "<i>syn-endo</i>" ~ 4
    ),
  )  %>%
  separate_wider_delim(
    cols = `Level of Theory`,
    delim = "/",
    names = c("Method", "Basis Set")
  ) %>%
  mutate(
    cardinal_number = sapply(`Basis Set`, cardinal_number)
  ) 

CBS <- plot_data %>%
  filter(`Basis Set` == "CBS") %>%
  rename(
    CBS_SCF = SCF,
    CBS_CORR = CORR,
  ) %>%
  select(
    Source,
    CBS_SCF,
    CBS_CORR
  )

QZ <- plot_data %>%
  filter(`Basis Set` == "ano-pVQZ") %>%
  rename(
    QZ_SCF = SCF,
    QZ_CORR = CORR,
  ) %>%
  select(
    Source,
    QZ_SCF,
    QZ_CORR
  )

plot_data <- plot_data %>%
  left_join(CBS) %>%
  left_join(QZ)


CCSD_energies %>%
  filter(`Level of Theory` == "CBS") %>%
  mutate(
    "Conformation" = gsub("<.{1,4}>", "", Source),
    "Extrapolated SCF Energy" = SCF,
    "Extrapolated Correlation Energy" = CORR,
    "DLPNO Correlation Correction" = correction,
    "Total CBS Energy" = TOTAL,
    .keep = "none"
  ) %>%
  arrange(`Total CBS Energy`) %>%
  write_csv(
    extrapolate_table_path
  )


```


### Extrapolation Plots
#### Plot Reaction Energy Extrapolation

```{r Plot Reaction Energy Extrapolation}

rxn_energy_data <- plot_data %>%
  filter(`Critical Point` == "Minimum")

plot <- rxn_energy_data %>%
  ggplot(
    aes(
      x = cardinal_number,
      shape = Method
    )
  ) +
  geom_point(
    data = rxn_energy_data %>%
      filter(cardinal_number >= 2, cardinal_number < 7),
    aes(
      y= CORR,
      colour = "CORR"
    ),
    size = 2) +
  geom_point(
    data = rxn_energy_data %>%
      filter(cardinal_number > 2, cardinal_number < 7),
    aes(
      y= SCF,
      colour = "SCF"
    ),
    size = 2) +
  geom_point(
    data = rxn_energy_data %>%
      filter(cardinal_number > 2),
    aes(
      y= TOTAL,
      colour = "TOTAL"
    ),
    size = 2
    ) +
  geom_point(
    data = rxn_energy_data %>%
      filter(is.infinite(cardinal_number)),
    aes(
      y= TOTAL,
      colour = "TOTAL",
      shape = "EP3"
    ),
    size = 2
    ) +
  geom_smooth(
    data = rxn_energy_data %>%
      filter(cardinal_number == 3 | cardinal_number == 4),
    aes(
      y = extrapolate_CORR(cardinal_number, CBS_CORR, QZ_CORR),
      group = Method,
      colour = "CORR",
      linetype = "Extrapolation"
    ),
    method = "lm",
    fullrange = TRUE,
    formula = y ~ I(1/x^beta),
    se = FALSE,
    linewidth = 0.5,
  ) +
  geom_smooth(
    data = rxn_energy_data %>%
      filter(cardinal_number == 3 | cardinal_number == 4),
    aes(
      y = extrapolate_SCF(cardinal_number, CBS_SCF, QZ_SCF),
      group = Method,
      colour = "SCF",
      linetype = "Extrapolation"
    ),
    method = "lm",
    fullrange = TRUE,
    formula = y ~ exp(-alpha*sqrt(x)),
    se = FALSE,
    linewidth = 0.5,
  ) +
  geom_smooth(
    data = rxn_energy_data %>%
      filter(cardinal_number == 3 | cardinal_number == 4),
    aes(
      y = extrapolate_both(cardinal_number, CBS_CORR, QZ_CORR, CBS_SCF, QZ_SCF),
      group = Method,
      colour = "TOTAL",
      linetype = "Extrapolation"
    ),
    method = "lm",
    fullrange = TRUE,
    formula = y ~ exp(-alpha*sqrt(x))+I(1/x^beta),
    se = FALSE,
    linewidth = 0.5,
  ) +
  geom_hline(
    aes(
      yintercept = 0
    ),
    colour = "black",
    linetype = 1,
    linewidth = 0.25
  ) +
  
  geom_hline(
    aes(
      yintercept = CBS_CORR,
      colour = "CORR",
      linetype = "CBS Limit"
    )
  ) +
  geom_hline(
    aes(
      yintercept = CBS_SCF,
      colour = "SCF",
      linetype = "CBS Limit"
    )
  ) +
  geom_hline(
    aes(
      yintercept = CBS_SCF + CBS_CORR,
      colour = "TOTAL",
      linetype = "CBS Limit"
    )
  ) +
  geom_segment(
    aes(
      y = SCF + CORR,
      yend = SCF + CORR + correction,
      colour = "Correction",
      linetype = "Correction"
    ),
    arrow = arrow(
      type = "closed",
      length = unit(2, "pt")
    ),
    linewidth = 1
  )+
  geom_segment(
    aes(
      y = CORR -  deviation,
      yend = CORR ,
      colour = "Correction",
      linetype = "Correction"
    ),
    arrow = arrow(
      type = "closed",
      length = unit(2, "pt")
    ),
    linewidth = 1
  )+
  scale_x_continuous(
    name = "Cardinal Number",
    oob = scales::squish_infinite,
    limits = c(2,5)
    
  ) +
  scale_y_continuous(
    name = "ΔE",
    breaks = seq(-4, 30, 2),
  )+
  scale_color_locuszoom(
    name = "Energy Component",
    labels = c(
      "CORR" = "ΔE<sub>corr</sub>",
      "SCF" = "ΔE<sub>HF</sub>",
      "TOTAL" = "ΔE<sub>HF</sub>+ΔE<sub>corr</sub>",
      "Correction" = "ΔΔE<sup>DLPNO</sup>"
    ),
    limits = c(
      "SCF",
      "CORR",
      "TOTAL",
      "Correction"
    )
  )+
  scale_linetype_manual(
    values = c(
      "Extrapolation" = 1,
      "CBS Limit" = 2,
      "Correction" = 1
    ),
  ) +
  scale_shape(
    name = "Method",
    limits = c(
      "CCSD(T)",
      "DLPNO-CCSD(T)",
      "EP3" = "EP3"
    )
  ) +
  guides(
    colour = guide_legend(
      name = "Energy Component",
    ),
    shape = guide_legend(
      name = "Method",
    ),
    linetype = guide_none(),
  )+
    facet_wrap(
     ~Source, 
     nrow = 1,
    ) +
  theme_ipsum(
    base_size = 8*.pt,
    strip_text_size = 8*.pt,
    axis_text_size = 8*.pt,
    axis_title_size = 10*.pt,
    axis_title_just = "cm",
    plot_margin = margin(0,0,0,0)
  )+
  theme(
    legend.title = element_text(
      hjust = 0
    ),
    legend.title.position = "top",
    legend.text = element_markdown(
      margin = margin(t = 3, b = 3)
    ),
    strip.placement = "inside",
    strip.text.x.top = element_markdown(
      angle = 0,
      hjust = 0.5
    ),
    panel.spacing.x = unit(5, "mm"),
    panel.grid.minor.x = element_blank(),
  )

plot

ggsave(
  extrapolate_rxn_energy_plot_path,
  plot,
  height = unit(8, "cm"), 
  width = unit(15.92, "cm"),
  dpi = 600
)

```

#### Plot Barrier Height Extrapolation

```{r Plot Barrier Height Extrapolation}

rxn_barrier_data <- plot_data %>%
  filter(`Critical Point` == "TS") %>%
  mutate(
    Source = factor(
      Source,
      levels = 
        c(
          "<i>anti-exo</i>",
          "<i>syn-exo</i>",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>"
      )
    )
  )

plot <- rxn_barrier_data %>%
  ggplot(
    aes(
      x = cardinal_number,
      shape = Method
    )
  ) +
  geom_point(
    data = rxn_barrier_data %>%
      filter(cardinal_number >= 2, cardinal_number < 7),
    aes(
      y= CORR,
      colour = "CORR"
    ),
    size = 2) +
  geom_point(
    data = rxn_barrier_data %>%
      filter(cardinal_number > 2, cardinal_number < 7),
    aes(
      y= SCF,
      colour = "SCF"
    ),
    size = 2) +
  geom_point(
    data = rxn_barrier_data %>%
      filter(cardinal_number > 2),
    aes(
      y= TOTAL,
      colour = "TOTAL"
    ),
    size = 2
    ) +
  geom_point(
    data = rxn_barrier_data %>%
      filter(is.infinite(cardinal_number)),
    aes(
      y= TOTAL,
      colour = "TOTAL",
      shape = "EP3"
    ),
    size = 2
    ) +
  geom_smooth(
    data = rxn_barrier_data %>%
      filter(cardinal_number == 3 | cardinal_number == 4),
    aes(
      y = extrapolate_CORR(cardinal_number, CBS_CORR, QZ_CORR),
      group = Method,
      colour = "CORR",
      linetype = "Extrapolation"
    ),
    method = "lm",
    fullrange = TRUE,
    formula = y ~ I(1/x^beta),
    se = FALSE,
    linewidth = 0.5,
  ) +
  geom_smooth(
    data = rxn_barrier_data %>%
      filter(cardinal_number == 3 | cardinal_number == 4),
    aes(
      y = extrapolate_SCF(cardinal_number, CBS_SCF, QZ_SCF),
      group = Method,
      colour = "SCF",
      linetype = "Extrapolation"
    ),
    method = "lm",
    fullrange = TRUE,
    formula = y ~ exp(-alpha*sqrt(x)),
    se = FALSE,
    linewidth = 0.5
  ) +
  geom_smooth(
    data = rxn_barrier_data %>%
      filter(cardinal_number == 3 | cardinal_number == 4),
    aes(
      y = extrapolate_both(cardinal_number, CBS_CORR, QZ_CORR, CBS_SCF, QZ_SCF),
      group = Method,
      colour = "TOTAL",
      linetype = "Extrapolation"
    ),
    method = "lm",
    fullrange = TRUE,
    formula = y ~ exp(-alpha*sqrt(x))+I(1/x^beta),
    se = FALSE,
    linewidth = 0.5
  ) +
  geom_hline(
    aes(
      yintercept = 0
    ),
    colour = "black",
    linetype = 1,
    linewidth = 0.25
  ) +
  
  geom_hline(
    aes(
      yintercept = CBS_CORR,
      colour = "CORR",
      linetype = "CBS Limit"
    )
  ) +
  geom_hline(
    aes(
      yintercept = CBS_SCF,
      colour = "SCF",
      linetype = "CBS Limit"
    )
  ) +
  geom_hline(
    aes(
      yintercept = CBS_SCF + CBS_CORR,
      colour = "TOTAL",
      linetype = "CBS Limit"
    )
  ) +
  geom_segment(
    aes(
      y = SCF + CORR,
      yend = SCF + CORR + correction,
      colour = "Correction",
      linetype = "Correction"
    ),
    arrow = arrow(
      type = "closed",
      length = unit(2, "pt")
    ),
    linewidth = 1
  )+
  geom_segment(
    aes(
      y = CORR -  deviation,
      yend = CORR ,
      colour = "Correction",
      linetype = "Correction"
    ),
    arrow = arrow(
      type = "closed",
      length = unit(2, "pt")
    ),
    linewidth = 1
  )+
  scale_x_continuous(
    name = "Cardinal Number",
    oob = scales::squish_infinite,
    limits = c(2,5)
    
  ) +
  scale_y_continuous(
    name = "ΔE",
    breaks = seq(-4, 30, 2),
  )+
  scale_color_locuszoom(
    name = "Energy Component",
    labels = c(
      "CORR" = "ΔE<sub>corr</sub>",
      "SCF" = "ΔE<sub>HF</sub>",
      "TOTAL" = "ΔE<sub>HF</sub>+ΔE<sub>corr</sub>",
      "Correction" = "ΔΔE<sup>DLPNO</sup>"
    ),
    limits = c(
      "SCF",
      "CORR",
      "TOTAL",
      "Correction"
    )
  )+
  scale_linetype_manual(
    values = c(
      "Extrapolation" = 1,
      "CBS Limit" = 2,
      "Correction" = 1
    ),
  ) +
  scale_shape(
    name = "Method",
    limits = c(
      "CCSD(T)",
      "DLPNO-CCSD(T)",
      "EP3" = "EP3"
    )
  ) +
  guides(
    colour = guide_legend(
      name = "Energy Component",
    ),
    shape = guide_legend(
      name = "Method",
    ),
    linetype = guide_none(),
  )+
    facet_wrap(
     ~Source, 
     nrow = 1,
    ) +
  theme_ipsum(
    base_size = 8*.pt,
    strip_text_size = 8*.pt,
    axis_text_size = 8*.pt,
    axis_title_size = 10*.pt,
    axis_title_just = "cm",
    plot_margin = margin(0,0,0,0)
  )+
  theme(
    legend.title = element_text(
      hjust = 0
    ),
    legend.title.position = "top",
    legend.text = element_markdown(
      margin = margin(t = 3, b = 3)
    ),
    strip.placement = "inside",
    strip.text.x.top = element_markdown(
      angle = 0,
      hjust = 0.5
    ),
    panel.spacing.x = unit(5, "mm"),
    panel.grid.minor.x = element_blank(),
  )

plot

ggsave(
  extrapolate_barrier_plot_path,
  plot,
  height = unit(8, "cm"), 
  width = unit(15.92, "cm"),
  dpi = 600
)

```

## DFT

### Import Properties

```{r import DFT Properies}

DFT_energies <- tibble()

for (i in 1:length(critical_points$name)) {
  for (j in 1:length(functionals)) {
    for (k in 1:length(basis_sets)) {
      path <- paste0(
        DFT_data_dir,
        critical_points$name[i],
        "_",
        functionals[j],
        "_",
        basis_sets[k],
        ".property.json"
      )
      
      json <- read_json(path)
      
      row <- tibble(
        "Source" = critical_points$name[i],
        "Functional" = functionals[j],
        "Basis Set" = basis_sets[k],
        "Critical Point" = critical_points$critical_point[i],
        "SCF_ENERGY" = json[["Geometry_1"]][["SCF_Energy"]][["SCF_ENERGY"]],
        "EEXCHANGE" = json[["Geometry_1"]][["DFT_Energy"]][["EEXCHANGE"]],
        "ECORR" = json[["Geometry_1"]][["DFT_Energy"]][["ECORR"]],
        "ECNL" = json[["Geometry_1"]][["DFT_Energy"]][["ECNL"]],
        "EXC" = json[["Geometry_1"]][["DFT_Energy"]][["EXC"]],
        "FINALEN" = json[["Geometry_1"]][["DFT_Energy"]][["FINALEN"]],
        "MP2CORR" = json[["Geometry_1"]][["MP2_Energies"]][["CORRENERGY"]],
        "MP2TOTALENERGY" = json[["Geometry_1"]][["MP2_Energies"]][["TOTALENERGY"]],
        "VDW" = json[["Geometry_1"]][["VdW_Correction"]][["VDW"]],
        "TOTALENERGY" = json[["Geometry_1"]][["Calculation_Info"]][["TOTALENERGY"]]
      ) %>%
        mutate(
          Functional = gsub(
            "_",
            "-",
            Functional
          )
        )
      
      DFT_energies <- DFT_energies %>%
        bind_rows(row)
    }
  }
}

DFT_energies <- DFT_energies %>% mutate(
    Source = case_match(
      Source,
      "anti-exo" ~ "<i>anti-exo</i>",
      "syn-exo" ~ "<i>syn-exo</i>" ,
      "anti-endo" ~ "<i>anti-endo</i>",
      "syn-endo" ~ "<i>syn-endo</i>",
      "transG_g-exo" ~ "<i>trans</i>-G<sub>γ</sub>",
      "transG_g-endo" ~ "<i>trans</i>-<sup>γ</sup>G",
      "cisD_g-exo" ~ "<i>cis</i>-D<sub>γ</sub>",
      "cisA_g-endo" ~ "<i>cis</i>-<sup>γ</sup>A",
      .default = Source
    )
  )

DFT_energies <- DFT_energies %>% 
  pivot_longer(
    cols = SCF_ENERGY:MP2TOTALENERGY,
    names_to = "Component",
    values_to = "Energy"
  )

dft_reference <- DFT_energies %>% 
  filter(
    Source == "<i>trans</i>-G<sub>γ</sub>"
    ) %>%
  rename("Reference Energy" = Energy) %>%
  select(!Source)

DFT_energies <- DFT_energies %>% 
  left_join(
    dft_reference,
    by = c(
      "Functional",
      "Basis Set",
      "Component"
      )
    ) %>%
  mutate(
    `Relative Energy` = (Energy - `Reference Energy`)*627.5094740631, 
  Source = factor(
      Source,
      levels = 
        rev(c(
          "<i>trans</i>-G<sub>γ</sub>",
          "<i>trans</i>-<sup>γ</sup>G",
          "<i>cis</i>-D<sub>γ</sub>",
          "<i>cis</i>-<sup>γ</sup>A",
          "<i>anti-exo</i>",
          "<i>syn-exo</i>",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>"
        )
      
    ) )
  )


rm(
  json,
  row
  )


```

### Plot DFT error

```{r Plot DFT error}

DFT_Error <- DFT_energies %>%
  filter(
    Component == "TOTALENERGY"
  ) %>%
  left_join(
    CBS_Energies,
    by = c(
      "Source"
      )
  ) %>%
  mutate(
   Error =  `Relative Energy`- CBS_REFERENCE_ENERGY
  )


plot <- DFT_Error %>%
  pivot_wider(
    id_cols = Source | Functional | `Critical Point`,
    names_from = `Basis Set`,
    values_from = Error
  ) %>%
  mutate(
    Source = factor(
      Source,
      levels = 
        c(
          "<i>trans</i>-G<sub>γ</sub>",
          "<i>trans</i>-<sup>γ</sup>G",
          "<i>cis</i>-D<sub>γ</sub>",
          "<i>cis</i>-<sup>γ</sup>A",
          "<i>anti-exo</i>",
          "<i>syn-exo</i>",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>"
        )
      
    ) ,
    Functional = case_match(
      Functional,
      "r2SCAN-D3BJ" ~ "r<sup>2</sup>SCAN-D3(BJ).mGGA",
      "B97M-V" ~ "B97M-V.mGGA",
      "B97M-D4" ~ "B97M-D4.mGGA",
      "PBE0-D3BJ" ~ "PBE0-D3BJ.Hybrid GGA",
      "M062X-D3ZERO" ~ "M06-2X-D3(0).Hybrid mGGA",
      "wB97X-D4rev" ~ "<i>ω</i>B97X-D4rev.Range-Separated Hybrid",
      "wB97X-V" ~ "<i>ω</i>B97X-V.Range-Separated Hybrid",
      "wB97M-D4rev" ~ "<i>ω</i>B97M-D4rev.Range-Separated Hybrid",
      "wB97M-V" ~ "<i>ω</i>B97M-V.Range-Separated Hybrid",
      "DSD-BLYP-D3BJ" ~ "DSD-BLYP-D3(0).Double Hybrid"
    ),
    Functional = factor(
      Functional, 
      levels = c(
        "r<sup>2</sup>SCAN-D3(BJ).mGGA",
        "B97M-D4.mGGA",
        "B97M-V.mGGA",
        "PBE0-D3BJ.Hybrid GGA",
        "M06-2X-D3(0).Hybrid mGGA",
        "<i>ω</i>B97X-D4rev.Range-Separated Hybrid",
        "<i>ω</i>B97X-V.Range-Separated Hybrid",
        "<i>ω</i>B97M-D4rev.Range-Separated Hybrid",
        "<i>ω</i>B97M-V.Range-Separated Hybrid",
        "DSD-BLYP-D3(0).Double Hybrid"
      )
    )
  ) %>%
  filter(
    !grepl("D4rev",Functional)
  ) %>%
  ggplot(
    aes(
      x = Functional,
      y = `def2-QZVPP`,
      fill = Functional
    )
  ) +
  geom_col(
  ) +
  scale_x_discrete(
    name = "Conformation",
    limits = ~rev(.x),
    expand = expansion(add = c(1, 1))
  )+
  scale_y_continuous(
    name = "ΔE<sub>DFT/def2-QZVPP</sub> - ΔE<sub>CCSD(T)/CBS</sub>",
    breaks = seq(-3, 3, 0.5)
  ) +
  #scale_fill_locuszoom()+
  scale_fill_viridis_d(
    option = "H"
  )+
  coord_flip() +
  guides(
    fill = guide_legend_group(
      key = key_group_split(sep = "\\.", reverse = TRUE),
      position = "right",
    ),
    y = guide_axis(
    )
  )+
  facet_wrap(
    ~Source,
    ncol = 1,
    strip.position = "left",
    axes = "all_x",
    axis.labels = "margins"
  ) +
  theme_ipsum(
    base_size = 8*.pt,
    #axis_title_family = "serif",
    strip_text_size = 8*.pt,
    axis_text_size = 8*.pt,
    axis_title_size = 10*.pt,
    axis_title_just = "cm",
    plot_margin = margin(0,0,0,0)
  )+ 
  theme(
    panel.spacing = unit(-1, "mm"),
    axis.text.y = element_blank(),
    strip.text.y.left = element_markdown(
      hjust = 1,
      vjust = 0.5,
      angle = 0
    ),
    panel.grid.major.y = element_blank(),
    axis.line.x = element_line(
      linewidth = 0.25
    ),
    legend.justification = c(0,0.5),
    legend.title.position = "left",
    legend.title = element_text(
      angle = 90,
      hjust = 0.5,
      size = 10*.pt
    ),
    legendry.legend.subtitle.position = "top",
    legendry.legend.subtitle = element_text(
      angle = 0,
      hjust = 0,
      size = 8*.pt
    ),
    legend.text = element_markdown(
      angle = 0,
      hjust = 0
    ),
    legend.text.position = "right",
    axis.title.x = element_markdown(
      family = "serif"
    )
  )

plot

ggsave(
  DFT_error_plot_path,
  plot,
  height = unit(10, "cm"), 
  width = unit(15.92, "cm"),
  dpi = 600
)


```


### Basis set dependance 

#### Plot reaction energy basis set dependance

```{r Plot reaction energy basis set dependance}


plot <- DFT_Error %>%
  mutate(
    Source = factor(
      Source,
      levels = 
        c(
          "<i>trans</i>-G<sub>γ</sub>",
          "<i>trans</i>-<sup>γ</sup>G",
          "<i>cis</i>-D<sub>γ</sub>",
          "<i>cis</i>-<sup>γ</sup>A",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>",
          "<i>anti-exo</i>",
          "<i>syn-exo</i>"
        )
      
    ),
    Functional = case_match(
      Functional,
      "r2SCAN-D3BJ" ~ "r<sup>2</sup>SCAN-D3(BJ).mGGA",
      "B97M-D4" ~ "B97M-D4.mGGA",
      "B97M-V" ~ "B97M-V.mGGA",
      "PBE0-D3BJ" ~ "PBE0-D3BJ.Hybrid GGA",
      "M062X-D3ZERO" ~ "M06-2X-D3(0).Hybrid mGGA",
      "wB97X-D4rev" ~ "<i>ω</i>B97X-D4rev.Range-Separated Hybrid",
      "wB97X-V" ~ "<i>ω</i>B97X-V.Range-Separated Hybrid",
      "wB97M-D4rev" ~ "<i>ω</i>B97M-D4rev.Range-Separated Hybrid",
      "wB97M-V" ~ "<i>ω</i>B97M-V.Range-Separated Hybrid",
      "DSD-BLYP-D3BJ" ~ "DSD-BLYP-D3(0).Double Hybrid"
    ),
    Functional = factor(
      Functional, 
      levels = c(
        "r<sup>2</sup>SCAN-D3(BJ).mGGA",
        "B97M-D4.mGGA",
        "B97M-V.mGGA",
        "PBE0-D3BJ.Hybrid GGA",
        "M06-2X-D3(0).Hybrid mGGA",
        "<i>ω</i>B97X-D4rev.Range-Separated Hybrid",
        "<i>ω</i>B97X-V.Range-Separated Hybrid",
        "<i>ω</i>B97M-D4rev.Range-Separated Hybrid",
        "<i>ω</i>B97M-V.Range-Separated Hybrid",
        "DSD-BLYP-D3(0).Double Hybrid"
      )
    ),
  ) %>%
  filter(
    !grepl("D4",Functional),
    `Critical Point` == "Minimum"
  ) %>% 
  ggplot(
    aes(
      x = `Basis Set`,
      y = Error,
      colour = Functional,
       group = Functional
    )
  ) +
  geom_hline(
    aes(yintercept = 0),
    colour = "black",
    linewidth = 0.5,
    alpha = 0.5
  ) +
  geom_point(
    size = 3
  ) +
  geom_line(
    linewidth = 1.5
  ) +
  scale_colour_viridis_d(
    option = "H"
  ) +
  guides(
    colour = guide_legend_group(
      key = key_group_split(sep = "\\.", reverse = TRUE)
    ),
  )+
  scale_x_discrete(
    name = "Cardinal Number",
    limits = c(
      "def2-TZVPP",
      "def2-QZVPP"
      ),
    labels = c(
      "def2-TZVPP" = "3",
      "def2-QZVPP" = "4"
    ),
  )+
  scale_y_continuous(
    name = expression(
        Delta*E[DFT]-Delta*E[CCSD(T)/CBS]
      ),
    breaks = seq(-3, 3, 0.2),
  ) +
  facet_wrap(
    ~Source,
    nrow = 1,
    axes = "all_y",
    axis.labels = "margins"
  ) +
  theme_ipsum(
    base_size = 8*.pt,
    strip_text_size = 8*.pt,
    axis_text_size = 8*.pt,
    axis_title_size = 10*.pt,
    axis_title_just = "cm",
    plot_margin = margin(0,0,0,0)
  ) +
  theme(
    axis.text.y = element_markdown(),
    axis.line.y = element_line(
      linewidth = 0.25
    ),
    panel.grid.major.x = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(-2, "mm"),
    strip.text.x.top = element_markdown(
      angle = 0,
      vjust = 0,
      hjust = 0.5,
    ),
    legend.justification = c(0,0.5),
    legend.title.position = "left",
    legend.title = element_text(
      angle = 90,
      hjust = 0.5,
      size = 10*.pt
    ),
    legendry.legend.subtitle.position = "top",
    legendry.legend.subtitle = element_text(
      angle = 0,
      hjust = 0,
      size = 8*.pt
    ),
    legend.text = element_markdown(
      angle = 0,
      hjust = 0
    ),
    legend.text.position = "right",
  )

plot
  
ggsave(
  DFT_rxn_basis_set_plot_path,
  plot,
  height = unit(8, "cm"), 
  width = unit(15.92, "cm")
)


```

#### Plot barrier height basis set dependance


```{r Plot barrier height basis set dependance}

plot <- DFT_Error %>%
mutate(
    Source = factor(
      Source,
      levels = 
        c(
          "<i>trans</i>-G<sub>γ</sub>",
          "<i>trans</i>-<sup>γ</sup>G",
          "<i>cis</i>-D<sub>γ</sub>",
          "<i>cis</i>-<sup>γ</sup>A",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>",
          "<i>anti-exo</i>",
          "<i>syn-exo</i>"
        )
      
    ),

    Functional = case_match(
      Functional,
      "r2SCAN-D3BJ" ~ "r<sup>2</sup>SCAN-D3(BJ).mGGA",
      "B97M-D4" ~ "B97M-D4.mGGA",
      "B97M-V" ~ "B97M-V.mGGA",
      "PBE0-D3BJ" ~ "PBE0-D3BJ.Hybrid GGA",
      "M062X-D3ZERO" ~ "M06-2X-D3(0).Hybrid mGGA",
      "wB97X-D4rev" ~ "<i>ω</i>B97X-D4rev.Range-Separated Hybrid",
      "wB97X-V" ~ "<i>ω</i>B97X-V.Range-Separated Hybrid",
      "wB97M-D4rev" ~ "<i>ω</i>B97M-D4rev.Range-Separated Hybrid",
      "wB97M-V" ~ "<i>ω</i>B97M-V.Range-Separated Hybrid",
      "DSD-BLYP-D3BJ" ~ "DSD-BLYP-D3(0).Double Hybrid"
    ),
    Functional = factor(
      Functional, 
      levels = c(
        "r<sup>2</sup>SCAN-D3(BJ).mGGA",
        "B97M-D4.mGGA",
        "B97M-V.mGGA",
        "PBE0-D3BJ.Hybrid GGA",
        "M06-2X-D3(0).Hybrid mGGA",
        "<i>ω</i>B97X-D4rev.Range-Separated Hybrid",
        "<i>ω</i>B97X-V.Range-Separated Hybrid",
        "<i>ω</i>B97M-D4rev.Range-Separated Hybrid",
        "<i>ω</i>B97M-V.Range-Separated Hybrid",
        "DSD-BLYP-D3(0).Double Hybrid"
      )
    ),
  ) %>%
  filter(
    !grepl("D4",Functional),
    `Critical Point` == "TS"
  ) %>% 
  ggplot(
    aes(
      x = `Basis Set`,
      y = Error,
      colour = Functional,
       group = Functional
    )
  ) +
  geom_hline(
    aes(yintercept = 0),
    colour = "black",
    linewidth = 0.5,
    alpha = 0.5
  ) +
  geom_point(
    size = 3
  ) +
  geom_line(
    linewidth = 1.5
  ) +
  scale_colour_viridis_d(
    option = "H"
  ) +
  guides(
    colour = guide_legend_group(
      key = key_group_split(sep = "\\.", reverse = TRUE)
    ),
  )+
  scale_x_discrete(
    name = "Cardinal Number",
    limits = c(
      "def2-TZVPP",
      "def2-QZVPP"
      ),
    labels = c(
      "def2-TZVPP" = "3",
      "def2-QZVPP" = "4"
    ),
  )+
  scale_y_continuous(
    name = expression(
        Delta*E[DFT]-Delta*E[CCSD(T)/CBS]
      ),
    breaks = seq(-3, 3, 0.2),
  ) +
  facet_wrap(
    ~Source,
    nrow = 1,
    axes = "all_y",
    axis.labels = "margins"
  ) +
  theme_ipsum(
    base_size = 8*.pt,
    strip_text_size = 8*.pt,
    axis_text_size = 8*.pt,
    axis_title_size = 10*.pt,
    axis_title_just = "cm",
    plot_margin = margin(0,0,0,0)
  ) +
  theme(
    axis.text.y = element_markdown(),
    axis.line.y = element_line(
      linewidth = 0.25
    ),
    panel.grid.major.x = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(-2, "mm"),
    strip.text.x.top = element_markdown(
      angle = 0,
      vjust = 0,
      hjust = 0.5,
    ),
    legend.justification = c(0,0.5),
    legend.title.position = "left",
    legend.title = element_text(
      angle = 90,
      hjust = 0.5,
      size = 10*.pt
    ),
    legendry.legend.subtitle.position = "top",
    legendry.legend.subtitle = element_text(
      angle = 0,
      hjust = 0,
      size = 8*.pt
    ),
    legend.text = element_markdown(
      angle = 0,
      hjust = 0
    ),
    legend.text.position = "right",
  )

plot

ggsave(
  DFT_barrier_basis_set_plot_path,
  plot,
  height = unit(10, "cm"), 
  width = unit(15.92, "cm")
)


```

## Dispersion Correction

### Prepare data

```{r  Dispersion Correction }

no_correction <- DFT_energies %>%
  filter(
    !grepl("V$", Functional)
  ) %>%
  separate_wider_regex(
    cols = Functional,
    patterns = c(Functional="^.*", "-", Correction=".*$")
  ) %>%
  select(!Correction)%>%
  mutate(Functional = paste(Functional, "None", sep = "-")) %>%
  pivot_wider(
    id_cols = Source | Functional | `Basis Set`,
    names_from = Component,
    values_from = Energy
  ) %>%
  mutate(
    VDW = 0,
    TOTALENERGY = FINALEN
  ) %>%
  pivot_longer(
    cols = SCF_ENERGY:MP2TOTALENERGY,
    names_to = "Component",
    values_to = "Energy"
  )

no_correction_reference <- no_correction %>%
  filter(
    Source == "<i>trans</i>-G<sub>γ</sub>"
  ) %>%
  rename(`Reference Energy` = Energy) %>%
  select(
    !Source
  )

no_correction <- no_correction %>%
  left_join(
    no_correction_reference,
    by = c(
      "Functional",
      "Basis Set",
      "Component"
    )
  ) %>%
  mutate(
    `Relative Energy` = (Energy - `Reference Energy`)*627.5094740631,
  )


dispersion_data <- DFT_energies %>%
  bind_rows(no_correction) %>% 
  filter(
    `Basis Set` == "def2-QZVPP",
    Component == "TOTALENERGY"
    ) %>%
  left_join(
    CBS_Energies,
    by = c(
      "Source"
      )
  ) %>%
  mutate(
   Error =   `Relative Energy`-CBS_REFERENCE_ENERGY,
    Source = factor(
      Source,
      levels = 
        c(
          "<i>trans</i>-G<sub>γ</sub>",
          "<i>trans</i>-<sup>γ</sup>G",
          "<i>cis</i>-D<sub>γ</sub>",
          "<i>cis</i>-<sup>γ</sup>A",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>",
          "<i>anti-exo</i>",
          "<i>syn-exo</i>"
        )
    )
  ) %>%
  separate_wider_regex(
    cols = Functional,
    patterns = c(Functional="^.*", "-", Correction=".*$")
  ) %>%
  mutate(
    Correction = case_match(
      Correction,
      "D3BJ" ~ "DFT-D",
      "D4" ~ "DFT-D",
      "D4rev" ~ "DFT-D",
      "D3ZERO" ~ "DFT-D",
      "V" ~ "DFT-NL (VV10)",
      .default = "None"
    ),
    Functional = case_match(
      Functional,
      "r2SCAN" ~ "r<sup>2</sup>SCAN",
      "B97M" ~ "B97M",
      "PBE0" ~ "PBE0",
      "M062X" ~ "M06-2X",
      "wB97X" ~ "<i>ω</i>B97X",
      "wB97M" ~ "<i>ω</i>B97M",
      "DSD-BLYP" ~ "DSD-BLYP"
    )
  ) %>%
  mutate(
    Functional = factor(
      Functional, 
      levels = c(
      "r<sup>2</sup>SCAN",
      "B97M",
      "PBE0",
      "M06-2X",
      "<i>ω</i>B97X",
      "<i>ω</i>B97M",
      "DSD-BLYP"
      )
    ),
    Correction = factor(
      Correction,
      levels = c(
      "None",
      "DFT-D",
      "DFT-NL (VV10)"
    )
    )
  ) 



None <- dispersion_data %>%
  filter(
    `Basis Set` == "def2-QZVPP",
    Correction == "None"
         ) %>%
  select(Source, Functional, `Basis Set`, Error) %>%
  rename(None_error = Error)

dispersion_data <- dispersion_data %>%
  left_join(None)
```

### Plot reaction energy dispersion correction

```{r Plot reaction energy dispersion correction}

plot <- dispersion_data %>% 
  filter(`Critical Point` == "Minimum") %>%
  ggplot(
    aes(
      x = Functional,
      y = Error,
      fill = Correction
    )
  ) +
  geom_col(
    position = position_dodge2(
      preserve = "single",
       reverse = FALSE),
    width = 0.5,
  )+
  geom_hline(
    aes(yintercept = 0),
    colour = "black",
    linewidth = 0.5,
    alpha = 0.5
  ) +
  scale_fill_locuszoom(
    name = "Dispersion Correction"
   ) +
  guides(
    fill = guide_legend(
      position = "top",
    )
    )+
  scale_y_continuous(
    name = expression(
        Delta*E[DFT/def2-QZVPP]-Delta*E[CCSD(T)/CBS]
      ),
    breaks = seq(-3, 3, 0.2)
  ) +
    facet_wrap(
    ~Source,
    nrow = 1,
    axes = "all_y",
    axis.labels = "margins"
  ) +
  theme_ipsum(
    base_size = 8*.pt,
    #axis_title_family = "serif",
    strip_text_size = 8*.pt,
    axis_text_size = 8*.pt,
    axis_title_size = 10*.pt,
    axis_title_just = "cm",
    plot_margin = margin(0,0,0,0)
  )+
  theme(
    axis.line.y = element_line(
      linewidth = 0.25
    ),
    panel.spacing = unit(-2, "mm"),
    strip.text = element_markdown(
      hjust = 0.5
    ),
    axis.text.x = element_markdown(
      angle = -90,
      hjust = 0,
      vjust = 0.5
    ),
    panel.grid.major.x = element_blank(),
    legend.title.position = "top",
    legend.justification = c(0, 1),
  )

plot

ggsave(
  rxn_dispersion_plot_path,
  plot,
  height = unit(10, "cm"), 
  width = unit(15.92, "cm")
)

```
### Plot barrier height dispersion corrections

```{r Plot barrier height dispersion corrections}

plot <- dispersion_data %>% 
  filter(`Critical Point` == "TS") %>%
  mutate(
    Source = factor(
      Source,
      levels = 
        c(
          "<i>anti-exo</i>",
          "<i>syn-exo</i>",
          "<i>anti-endo</i>",
          "<i>syn-endo</i>"
      )
    )
  ) %>%

  ggplot(
    aes(
      x = Functional,
      y = Error,
      fill = Correction
    )
  ) +
  geom_col(
    position = position_dodge2(
      preserve = "single",
       reverse = FALSE),
    width = 0.5,
  )+
  geom_hline(
    aes(yintercept = 0),
    colour = "black",
    linewidth = 0.5,
    alpha = 0.5
  ) +
  scale_fill_locuszoom(
    name = "Dispersion Correction"
   ) +
  guides(
    fill = guide_legend(
      position = "top",
    )
    )+
  scale_y_continuous(
    name = expression(
        Delta*E[DFT/def2-QZVPP]-Delta*E[CCSD(T)/CBS]
      ),
    breaks = seq(-3, 3, 0.2)
  ) +
    facet_wrap(
    ~Source,
    nrow = 1,
    axes = "all_y",
    axis.labels = "margins"
  ) +
  theme_ipsum(
    base_size = 8*.pt,
    #axis_title_family = "serif",
    strip_text_size = 8*.pt,
    axis_text_size = 8*.pt,
    axis_title_size = 10*.pt,
    axis_title_just = "cm",
    plot_margin = margin(0,0,0,0)
  )+
  theme(
    axis.line.y = element_line(
      linewidth = 0.25
    ),
    panel.spacing = unit(-2, "mm"),
    strip.text = element_markdown(
      hjust = 0.5
    ),
    axis.text.x = element_markdown(
      angle = -90,
      hjust = 0,
      vjust = 0.5
    ),
    panel.grid.major.x = element_blank(),
    legend.title.position = "top",
    legend.justification = c(0, 1),
  )

plot

ggsave(
  barrier_dispersion_plot_path,
  plot,
  height = unit(15.92, "cm"), 
  width = unit(15.92, "cm")
)

```

